Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-08-29 Paper.Rmd
it never ends

@@

files <- dir()

files <- files[str_detect(files, "movie_.+")]

@@

## Removing All the Duplicated Reviews including the original since same reviews were written by differend user names
movies_data <- movies_data %>% 
  mutate(Rev_dup = duplicated(Review) | duplicated(Review, fromLast = TRUE)) %>% 
  filter(Rev_dup == 0)

## Words
movies_data <- movies_data %>% 
  mutate(Doc_ID = row_number())

@@

## Laptop Data
files <- dir()
files <- files[str_detect(dir(), "all_laptop_reviews.+")]
laptop_data <- map_dfr(files, read_csv, show_col_types = FALSE)
### Removing replicates that I couldn't detect earlier
laptop_data <- laptop_data %>% 
  filter(!Product_Name %in% c(
    'Samsung - Galaxy Book Pro 360 15.6" AMOLED Touch-Screen Laptop - Intel Evo Platform Core i7 - 16GB Memory - 1TB SSD - Mystic Navy',
    'ASUS - 14.0" Laptop - Intel Celeron N4020 - 4GB Memory - 64GB eMMC - Star Black - Star Black',
    'ASUS - 14" Chromebook - Intel Celeron N3350 - 4GB Memory - 32GB eMMC - Silver',
    'Samsung - Galaxy 13.3" 4K Ultra HD Touch-Screen Chromebook - Intel Core i5 - 8GB Memory - 256GB SSD - Mercury Gray'
  )) %>% 
  mutate(Product_Type = "Laptop")

@@

## Word Counts

search_goods <- search_goods %>% 
  mutate(Doc_ID = row_number())

@@

## Freshness (Timeline)

search_goods <- search_goods %>% 
  mutate(Date = as_date(mdy_hm(Date, locale = "english")))

@@

*"caricature, superstition, compost, misconception, grief, violation, scrub, omen, erratic, porcupine"*

@@

*"covenant, jovial, score, foundation, affirmation, reliable, mending, garden, luxurious, wit"*

@@

## Hypothesis Development and Method

@@

*H1: There is a U-Shaped relationship between Perceived Helpfulness and Review Rating. This U-Shape is stronger/weaker for Search/Experience Goods.*

@@

*H2: There is a positive relationship between logarithm of Review Length and Perceived Helpfulness. This effect is stronger for Search Goods than Experience Goods*.

@@

*H3: There is a negative linear interaction effect between Review Rating and the logarithm of the Review Length for both Search and Experience Goods.*

@@

*H4: There is a positive relationship between Perceived Helpfulness and Freshness of a Review for both Search and Experience Goods.*

@@

*H5: There is a positive relationship between the Proportion of Negative Words and Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*

\
*H6: There is a negative relationship between the Proportion of Positive Words and Perceived Helpfulness for both product types.*

Tobit Regression is selected as the method because of three reasons. First of all, dependent variable, perceived helpfulness, is defined in a continuous range from 0 to 1. The second reason as stated by @mudambi2010 is the potential selection bias in the sample. Unfortunately, it is not possible to know how many people read a particular review. Neither BestBuy nor IMDB discloses this information. Because of this, being included in a sample could be correlated with independent variables. For instance, potentially more voted reviews could attract more readers or readers could be drawn to reviews which have certain ratings. Lastly, there are many studies from the literature that used Tobit Regression as their research method [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019].

@@

\
--- --- --- ---

------------------------------------------------------------------------

------------------------------------------------------------------------

>>>>

Any website which offers online reviews for products were used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data from either websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data. They have their respective APIs and on top of that, it is relatively easier to scrape both websites. Additionally, both websites offer product reviews for a numerous different types of products. Amazon is a huge e-retailer and offers a wide range of items. IMDB is a home for both critic and user reviews of Movies and TV Shows. In some other studies local equivalents of Amazon was used as well. [@sun2019]. @cao2011 used data from CNET Download.com which is a software distributor.

@@

files <- dir()
files <- files[str_detect(files, "movie_.+")]

@@

## Removing All the Duplicated Reviews including the originals since same reviews were written by differend user names
movies_data <- movies_data %>% 
  mutate(Rev_dup = duplicated(Review) | duplicated(Review, fromLast = TRUE)) %>% 
  filter(Rev_dup == 0)

# Words
## Creating Review ID
movies_data <- movies_data %>% 
  mutate(Doc_ID = row_number())

@@

## Laptop Data
files <- dir()
files <- files[str_detect(dir(), "all_laptop_reviews.+")]

laptop_data <- map_dfr(files, read_csv, show_col_types = FALSE)

### Removing replicates that I couldn't detect earlier
laptop_data <- laptop_data %>% 
  filter(!Product_Name %in% c(
    'Samsung - Galaxy Book Pro 360 15.6" AMOLED Touch-Screen Laptop - Intel Evo Platform Core i7 - 16GB Memory - 1TB SSD - Mystic Navy',
    'ASUS - 14.0" Laptop - Intel Celeron N4020 - 4GB Memory - 64GB eMMC - Star Black - Star Black',
    'ASUS - 14" Chromebook - Intel Celeron N3350 - 4GB Memory - 32GB eMMC - Silver',
    'Samsung - Galaxy 13.3" 4K Ultra HD Touch-Screen Chromebook - Intel Core i5 - 8GB Memory - 256GB SSD - Mercury Gray'
  )) %>% 
  mutate(Product_Type = "Laptop")

@@

## Word Counts
### Creating Review IDs
search_goods <- search_goods %>% 
  mutate(Doc_ID = row_number())

@@

## Freshness (Timeline)
search_goods <- search_goods %>% 
  mutate(Date = as_date(mdy_hm(Date, locale = "english")))

@@

> *"caricature, superstition, compost, misconception, grief, violation, scrub, omen, erratic, porcupine"*

@@

> *"covenant, jovial, score, foundation, affirmation, reliable, mending, garden, luxurious, wit"*

@@

## Hypothesis Development

@@

***H1**: There is a U-Shaped relationship between Perceived Helpfulness and Review Rating. This U-Shape is stronger/weaker for Search/Experience Goods.*

@@

***H2**: There is a positive relationship between logarithm of Review Length and Perceived Helpfulness. This effect is stronger for Search Goods than Experience Goods*.

@@

***H3**: There is a negative linear interaction effect between Review Rating and the logarithm of the Review Length for both Search and Experience Goods.*

@@

***H4**: There is a positive relationship between Perceived Helpfulness and Freshness of a Review for both Search and Experience Goods.*

@@

***H5**: There is a positive relationship between the Proportion of Negative Words and Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*\
***H6**: There is a negative relationship between the Proportion of Positive Words and Perceived Helpfulness for both product types.*

## Research Methodology

Tobit model is also named as Censored Regression model. Censored data arises when there exist lower (censored from below) or upper (censored from above) or both lower and upper boundaries for the dependent variable. This type of data is fairly prevalent in Economics. For instance, in consumer economics there is no such thing as "negative consumption" or in labor economics there is no such thing as "negative work hours". Furthermore, there might be cases where some really high values could be recorded as "50,000 or more" because of the data collection design. Ordinary Least Squares can't take account of the censored observations in the data because it extrapolates lower and upper ends when it fits the model and this leads biased estimations.

Tobit regression approaches censored dependent variable problem from two angles. In a sense Tobit regression could be considered as the summation of Probit regression and Truncated regression. The probit side considers if a particular observation is above or below the given limit. If the observation, for example, is below the lower limit then it must be equal to the lower limit. If it is higher than the lower limit the problem turns to a normal regression. In this case, Perceived Helpfulness can be expressed such as this:

$$
y=
\begin{cases}
  0   & \text{if  $ \ y^* \le0$} \\
  y^* & \text{if $ \ 0< y^* <1$} \\
  1   & \text{if $ \ y^* \ge 1$}
\end{cases}
$$

Tobit Regression is selected as the analysis method because of three reasons. First of all, the dependent variable, perceived helpfulness, is defined in a continuous range from 0 to 1 since perceived helpfulness is a percentage as mentioned above. The second reason as stated by @mudambi2010 is the potential selection bias in the sample. Unfortunately, it is not possible to know how many people read a particular review. Neither BestBuy nor IMDB disclose this information. Because of this, being included in a sample could be correlated with independent variables. For instance, potentially more voted reviews could attract more readers or readers could be drawn to reviews which have certain ratings. Lastly, there are many studies from the literature that used Tobit Regression as their research method [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019].

@@
